A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2016-10-03 doc/paper1-submission/paper4.tex
typo.

\subsection{Subproblems}
In the \otlprob{} summary tree, the decomposition procedure produced
5,406 subproblems, but only 1,422 of these were non-trivial to solve.
If a subproblem contains only two tips it is trivial; 2,362 subproblems
were trivial in this way. Similarly, if a subproblem contains only
2 trees it is trivial to solve because the solution will simply be
all of the groupings from the first tree combined with all of the
groupings from the second tree that are compatible with the first
tree; 3,052 subproblems were trivial in this way. The subproblem with
the largest number of tips contained 946 tips. The largest subproblem,
in terms of the number of input trees (including the taxonomic tree)
that were relevant, had 16 trees. Without decomposition, the supertree
problem would have had 482 input trees and 41,226 leaves.

>>>>

\subsection{Subproblems}
In the \otlprop{} summary tree, the decomposition procedure produced
5,406 subproblems, but only 1,422 of these were non-trivial to solve.
If a subproblem contains only two tips it is trivial; 2,362 subproblems
were trivial in this way. Similarly, if a subproblem contains only
2 trees it is trivial to solve because the solution will simply be
all of the groupings from the first tree combined with all of the
groupings from the second tree that are compatible with the first
tree; 3,052 subproblems were trivial in this way. The subproblem with
the largest number of tips contained 946 tips. The largest subproblem,
in terms of the number of input trees (including the taxonomic tree)
that were relevant, had 16 trees. Without decomposition, the supertree
problem would have had 482 input trees and 41,226 leaves.
